Master Thesis

### 2024-06-21 output/documents/thesis_paper/paper.qmd
Added water quality analysis scripts

---
title: "Master Thesis"
subtitle: "Economics of Sustainability and the Environment"
author: "Felix Schulz"
format:
  pdf:
    toc: false
    number-sections: true
    link-citations: true
bibliography: "./Environmental Economics Project.bib"
---

@@

# Methodology

@@

>>>>

---
title: "Master Thesis"
subtitle: "Economics of Sustainability and the Environment"
author: "Felix Schulz"
format:
  pdf:
    toc: false
    number-sections: true
    link-citations: true
bibliography: "./Master Thesis.bib"
---

@@

# Sensor-measured pollution and deforestation

Regressing the deforestation rate on various sensor-measured indicators, I directly estimate the correlation between deforestation and river pollution. I set up a panel regression model with station- and year-fixed effects and two-way clustered standard errors.

 and outcome variable, In @fig-stations_deforestation_Ofe_Ycl I present the results of this analysis. I find that increased deforestation is associated with increased readings on all outcome variables. As one would expect, all estimated coefficients are decreasing in distance to the deforestation. However only

There is a range of possible factors impacting river pollution outside of deforestation-related mechanisms. To alleviate the concern that my estimates are driven by other trends in deforestation over time I estimate two-way fixed effects models and include results in Figure . This approach yields equivalent results, albeit lacking the statistical power given the limited intra-annual variation in the variables. I also dis

@@

{{< include /tables/reg_stations_deforestation_agg_2005.tex >}}

![](/figures/stations_deforestation_g5_share_Yfe_Ycl.png){#fig-stations_deforestation_Ofe_Ycl}
